Dependent Object Types

### 2012-08-08 article.tex
root.Nat  instead of Nat

\subsection{Polymorphic Lists}
Polymorphic lists can be expressed using an abstract type member for
the element type ($\mi{Elem}$). We can instantiate a refinement of the
list package to manipulate lists with a particular element type. We
can choose to make the lists invariant or covariant in the element
type by fixing the lower bound of the $\mi{Elem}$ re-declaration to
the upper bound or to $\Bot$, respectively.
\begin{align*}
&\mlnew {\mi{genLists}} {\Top \mlrefine g {\Ldecl {\mi{ListPackage}} \Bot {\Top \mlrefine p {\\\displaybreak[3]
&\ \Ldecl {\mi{Elem}} \Bot \Top\\
&\ \Ldecl {\mi{ListOfElement}} {g.\mi{List} \refine z {\Ldecl {\mi{Elem}} {p.\mi{Elem}} {p.\mi{Elem}}}} {\\&\gap\gap\gap\gap g.\mi{List} \refine z {\Ldecl {\mi{Elem}} {p.\mi{Elem}} {p.\mi{Elem}}}}\\
&\ \Ldecl {\mi{List}} \Bot {\Top \mlrefine z {\\\displaybreak[3]
&\ \gap \mdecl {\mi{isEmpty}} {\mi{root}.\mi{Unit}} {\mi{root}.\mi{Boolean}}\\
&\ \gap \mdecl {\mi{head}} {\mi{root}.\mi{Unit}} {g.\mi{Elem}}\\
&\ \gap \mdecl {\mi{tail}} {\mi{root}.\mi{Unit}} {g.\mi{ListOfElem}}\\
&\gap}}\\
&\ \mdecl {\mi{nil}} {\mi{root}.\mi{Unit}} {g.\mi{ListOfElem}}\\
&\ \mdecl {\mi{cons}} {g.\mi{Elem}} {g.\mi{ListOfElem}}\\
&}}}}{
\mlnew {\mi{natLists}} {{\mi{genLists}.\mi{ListPackage}} \mlrefine p { \Ldecl {\mi{Elem}} {\mi{Nat}} {\mi{Nat}} }\mlldefs{\\\displaybreak[3]
&\ {\mi{nil}}(u) = \ldots\\
&\ {\mi{cons}}(u) = \ldots\\
&}}}{
\ldots
}
\end{align*}

>>>>

\subsection{Polymorphic Lists}
Polymorphic lists can be expressed using an abstract type member for
the element type ($\mi{Elem}$). We can instantiate a refinement of the
list package to manipulate lists with a particular element type. We
can choose to make the lists invariant or covariant in the element
type by fixing the lower bound of the $\mi{Elem}$ re-declaration to
the upper bound or to $\Bot$, respectively.
\begin{align*}
&\mlnew {\mi{genLists}} {\Top \mlrefine g {\Ldecl {\mi{ListPackage}} \Bot {\Top \mlrefine p {\\\displaybreak[3]
&\ \Ldecl {\mi{Elem}} \Bot \Top\\\displaybreak[3]
&\ \Ldecl {\mi{ListOfElement}} {g.\mi{List} \refine z {\Ldecl {\mi{Elem}} {p.\mi{Elem}} {p.\mi{Elem}}}} {\\&\gap\gap\gap\gap g.\mi{List} \refine z {\Ldecl {\mi{Elem}} {p.\mi{Elem}} {p.\mi{Elem}}}}\\\displaybreak[3]
&\ \Ldecl {\mi{List}} \Bot {\Top \mlrefine z {\\\displaybreak[3]
&\ \gap \mdecl {\mi{isEmpty}} {\mi{root}.\mi{Unit}} {\mi{root}.\mi{Boolean}}\\\displaybreak[3]
&\ \gap \mdecl {\mi{head}} {\mi{root}.\mi{Unit}} {g.\mi{Elem}}\\\displaybreak[3]
&\ \gap \mdecl {\mi{tail}} {\mi{root}.\mi{Unit}} {g.\mi{ListOfElem}}\\\displaybreak[3]
&\gap}}\\\displaybreak[3]
&\ \mdecl {\mi{nil}} {\mi{root}.\mi{Unit}} {g.\mi{ListOfElem}}\\\displaybreak[3]
&\ \mdecl {\mi{cons}} {g.\mi{Elem}} {g.\mi{ListOfElem}}\\\displaybreak[3]
&}}}}{
\mlnew {\mi{natLists}} {{\mi{genLists}.\mi{ListPackage}} \mlrefine p {\\\displaybreak[3]
&\gap \Ldecl {\mi{Elem}} {\mi{root}.\mi{Nat}} {\mi{root}.\mi{Nat}} }\mlldefs{\\\displaybreak[3]
&\ {\mi{nil}}(u) = \ldots\\\displaybreak[3]
&\ {\mi{cons}}(u) = \ldots\\\displaybreak[3]
&}}}{
\ldots
}
\end{align*}
